\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}

\begin{document}

\centerline{\large \bf BO LAN}

\centerline{356 Princeton St., East Boston, MA, 02128; 857-350-7615}

\centerline{lan.b@husky.neu.edu; http://wealthlibre.info/blog}

\noindent

\centerline{\line(1,0){470}}

\medskip

\noindent{\large \bf SUMMARY:}

\noindent
Long term experiences in web server management, coding open source programs, and 3D designed would build an innovative and productive work environment. The diversity management and multi-language skills should be great for every communication position. Great accounting experience and financial skills would provide a benefit to corporations to manage costs, investments, and other financial transactions.

\medskip

\noindent{\large \bf EDUCATION:}

\noindent
{\bf Master of Science in Leadership: Financial Market and Institution} \hfill May 2014

\noindent
Northeastern University, Boston, MA

\smallskip

\noindent {\bf Certified General Accountant Students Program} \hfill  September 2008 -- Present

\noindent Beijing Branch of Certified General Accountants Association of Canada, Beijing, China

\smallskip

\noindent
{\bf Bachelor of Management in Financial Management} \hfill May 2011

\noindent
Accounting School, Huanghe Science and Technology College, Zhengzhou, Henan, China

\medskip

\noindent{\large \bf SKILLS:}

\noindent
{\bf Computer Design Skills:} Libreoffice, {\LaTeX}, Gimp, Inkscape, Kdenlive Video Editor, Audacity Audio Editor, Blender 3D, Emacs Text Editor, Scribus

\noindent
{\bf Information Technologies:} C/C++, Python, CSS, HTML, Javascript, SQL Database, GTK+, Google App Engine, Blener Game Engine, OGRE 3D Engine.

\noindent
{\bf Operating Systems:} GNU/Linux, Mac Os X

\noindent
{\bf Accounting \& Finance:} GAAP, Financial Statements, Journal Entries, Contribution Margin \& Cost Management, Auditing \& Working Paper, Consolidated financial statements, Investment Analysis

\noindent
{\bf Accounting \& Auditing Softwares:} SAGE Accpac, Caseware: Working Paper, GnuCash, Yongyou U8 Solution

\noindent
{\bf Languages:} English, Mandarin, Cantonese

\medskip

\noindent{\large \bf PROFESSIONAL EXPERIENCES:}

\noindent{\bf Nanning Bicycle Network Company-- http://www.nnzxc.com}  \hfill Nanning, Guangxi, China

\noindent \textit{\textbf{Co-founder, Organizer, Web manager}} \hfill October 2003 -- September 2011

\hangindent=0.7cm $\bullet$ Managed, operated, and promoted a commercial website which sells bikes. This website is used PHP, MySql technologies, and the Dicuz! bbs framework.

\hangindent=0.7cm $\bullet$ Taught athletes and other employees how to communicate, race, do business, promote the company under the information and international circumstance. Organized and hosted races and training events for professional athletes.

\medskip

\noindent{\bf Nanning Xiantong Electronic Commerce LLC.} \hfill Nanning, Guangxi, China

\noindent \textit{\textbf{Assistant Accountant, Cost Manager Assistant}} \hfill June 2010 -- September 2010

\hangindent=0.7cm $\bullet$ Recorded journal entries and assisted the accountant and other managers. Analyzed financial statements, and assisted managers for cost management decisions.

\hangindent=0.7cm $\bullet$ Classified and managed electronic inventories, and match cost accumulation to inventories.

\medskip

\noindent{\large \bf OTHER ACTIVITIES:}

\noindent{\bf Wealth \& Libre -- http://wealthlibre.info/} \hfill Boston, MA

\noindent \textit{\textbf{Indie Web Developer, Finance Analyst, Arts Designer}} \hfill December 2013 -- Present

\hangindent=0.7cm $\bullet$ Develop this web base on Python, CSS, Html5, and Javascript. Design art contents for this web by Gimp, Inkscape.

\hangindent=0.7cm $\bullet$ Write and release finance, leadership, and free software information through this web page.

\medskip

\noindent {\bf Northeastern University Cycling Team} \hfill Boston, MA

\noindent \textit{\textbf{Athlete, Organizer, Volunteer}} \hfill September 2011 -- Present

\hangindent=0.7cm $\bullet$ Organize, host riding and race at Eastern Collegiate Cycling Conference.

\hangindent=0.7cm $\bullet$ Race bike at Eastern Collegiate Cycling Conference.

\end{document}
